Political Polarization, Public Trust, and Healthcare Disparities: Unraveling COVID-19's Impact and Future Preparedness

### 2024-02-14 outputs/paper/paper.qmd
updated discussion

This begs the question as to why we are seeing these results. There isn't exactly a single answer to this question, however, we can certainly point out some considerable factors to this result.

## Influence of political polarization on adherence to health guidelines.

>>>>

This begs the question as to why we are seeing these results. There isn't exactly a single answer to this question, however, we can certainly point out some considerable factors to this result. These factors can be broken down into the influence of political polarization, the impact of government transparency which ties into the effect it also had on public trust, and the role of social vulnerabilities and healthcare access disparities. We should also look at how to address these potential factors by implementing strategies in the future in regards to data collection and sharing. It is important to also note we were able to identify some weaknesses in our research that should be evaluated in the future.

## Influence of political polarization on adherence to health guidelines
